Search-Based Test Data Generation for JavaScript Functions with DOM

### 2017-11-15 doc/icse2018/icse2018.tex
Uncommented boolean flag branch in isGameFinished example.

Table~\ref{tbl.case.studies} presents generic quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}). The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.

>>>>

Table~\ref{tbl.case.studies} presents common quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}). The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
